---
title: 'Data Science Capstone Project: Word Prediction'
author: "Danna Ashley J. Mayo"
date: "August 16, 2019 - Friday"
output:
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```
## Introduction {data-background=grad.jpg data-background-size=cover}
Objective:

The goal is to build  a product specifically a shiny application made using R to highlight the prediction algorithm that is built and to provide a user-friendly interface that can be accessed by others conveniently.

## How was it created? {data-background=grad.jpg data-background-size=cover}
- Preprocessed the data (removed unnecessary expressions not needed for prediction)</font>
- Stemmed the text corpus
- Created N-grams and Document Frequency Matrices from the corpus
- Tokenized the group of words for better word count
- Created functions to predict next word using the concept of n-gram and backoff modeling

<span style="color:#7C0000">Limitations:</span>

- <b><font size = "3">If the word or phrase entered in the text box is beyond the scope of the algorithm, it will produce or display "NA"s for all buttons. 
- Words more than three will predict the next word only based on the last two words of the whole phrase or sentence. This is because of the constraints from the n-gram model.</font></b>
```{r}
```
## Shiny Application: How does it work? {data-background=grad.jpg data-background-size=cover}
```{r}
library(png)
library(grid)
appimg <- readPNG('appss.PNG')
grid.raster(appimg)
```
<font size = "4">Reminder: The application is subject to limitations mentioned in the previous slide. </font>

## Sources {data-background=grad.jpg data-background-size=cover}
Shiny Application: https://dajmayo.shinyapps.io/WordPrediction/

Github Repository: https://github.com/dajmayo/Data-Science-Capstone-Project

Dataset: https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip
